Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-23 manuscript.Rmd

@@

@@

# Make variable types/names congruent for merging
# rename
library(magrittr)
ind_diffs_self %<>% 
  rename(PerUn = SubNum)

@@

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)
```

@@

@@

@@

    lm(ptrait ~ targSRrC + AvgtraitC,
              data = .x)

  }
                      )
         )
```

>>>>

> This project is really fabulously done - the output is very clear and readable. If you're planning on continuing the manuscript in r, have you thought about using [Pandoc](https://pandoc.org/MANUAL.html#citations) as your citation manager? I don't know if it's worth the learning curve from what I know about your relationship to these data, but it may be something to check out if you want :-)

@@

> Sourcing your functions from a separate R script is a really good idea - it helps clean your code AND makes the functions easier to find (a problem I have when I have more than 2 in a script)

@@

# Make variable types/names congruent for merging
# rename
require(magrittr) # If this is a late addition, I assume you'll put it up with your other libraries , but if you need specifically magrittr for the following scripts, I wonder if require() will make this more reproducible?
ind_diffs_self %<>% 
  rename(PerUn = SubNum)

@@

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE) %>% round(., 2),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE) %>% round(., 2),
) %>% knitr::kable()
```

@@

> I know you already know about Kable, but I added it (and rounded the data) above because it was a simple addition - feel free to keep or not (obviously).

@@

> These analyses are really solid anaylitic work and I'm very excited to see where they go from here! You'll know better than I what you want to do with these, but can the emmeans package be useful for lmer objects? I've only used it with glm objects but *love* its simplicity :)

@@

    lm(ptrait ~ targSRrC + AvgtraitC,
              data = .x)
  }
                      )
         )
```
